\textbf{Computational Fuzzy Extractors}

### 2013-05-17 trunk/CompFuzzExt.tex
Small changes to abstract

\begin{itemize}
\item\textbf{Negative Result:} Noise tolerance in fuzzy extractors is usually
achieved using an information reconciliation component called ``secure
sketch.'' The security of this component, which directly affects the
length of the resulting key, is subject to lower bounds from coding
theory.  We show that, even when defined computationally, secure
sketches are still subject to the same lower bounds. Specifically, we consider
two computational relaxations of the information-theoretic security requirement of secure sketches, using conditional HILL entropy and unpredictability entropy. For both cases we show  that computational secure sketches cannot outperform information-theoretic ones in the case of high-entropy Hamming metric sources.

@@

\bnote{There needs to be more linking language here.}
It seems natural to construct a computational fuzzy extractor using a sketch that retains computational entropy and then apply a randomness extractor~(extractors convert distributions with high computational entropy to pseudorandom).  In the next section, we show this paradigm is difficult to realize.

>>>>

\begin{itemize}
\item\textbf{Negative Result:} Noise tolerance in fuzzy extractors is usually
achieved using an information reconciliation component called a ``secure
sketch.'' The security of this component, which directly affects the
length of the resulting key, is subject to lower bounds from coding
theory.  We show that, even when defined computationally, secure
sketches are still subject to lower bounds from coding theory. Specifically, we consider
two computational relaxations of the information-theoretic security requirement of secure sketches, using conditional HILL entropy and unpredictability entropy. For both cases we show  that computational secure sketches cannot outperform the best information-theoretic secure sketches in the case of high-entropy Hamming metric sources.

@@

%\bnote{There needs to be more linking language here.}
%It seems natural to construct a computational fuzzy extractor using a sketch that retains computational entropy and then apply a randomness extractor~(extractors convert distributions with high computational entropy to pseudorandom).  In the next section, we show this paradigm is difficult to realize.
